### 2014-03-13 src/analysis.Rnw
update

>>>>

o.stats.sel.op$kind  <- ifelse(grepl('opsel:', o.stats.sel.op$operator), 'selection', 'operator')
r.stats.sel.op$kind  <- ifelse(grepl('opsel:', o.stats.sel.op$operator), 'selection', 'operator')

o.stats.sel.op$operator  <- gsub('_','',gsub('op.*:','', o.stats.sel.op$operator))
r.stats.sel.op$operator  <- gsub('_','',gsub('op.*:','', r.stats.sel.op$operator))

o.stats.sel.op <- o.stats.sel.op[,c(1,7,2,3,4,5,6)]
r.stats.sel.op <- r.stats.sel.op[,c(1,7,2,3,4,5,6)]

#o.stats.sel.one$sampling  <- gsub('_.*','', o.stats.sel.one$operator)
